---
title: "DH_BIO720_InClassWeek2"
output: html_document
---

1. In the first one x is set to 1, 1 is added to this variable, and then this output is printed (x). x is then 2 and 1 is added again, and the output printed. This repeats until x is set to 9, because the for includes (i in 1:9), x does not get set higher than 9 because this loop only repeats 9 times. For this example, x needs to be defined and then the for loop can be executed. 

In the second examples, a function is created. Similarly, in this for loop 1 gets added to x. However, this repeats ten times because the for loop includes (i in 1:10). A major difference in this examples is because it is a function you can call any number into countfun().

2.
```{r}
x <- NA
system.time( for (i in 1:10000) {
    print(i^2) 
})


x <- rep(NA, length = 10000)
system.time( for (i in 1:10000) {
    print(i^2) 
})

```



3. When you pre-allocate a vector it makes it faster. This is proven with above example. 


4. 
```{r}
rm(x)
x <- 1:10000
system.time(x <- x^2)
```

5. Vectorizing is an advantage( as it is faster) and when possible you should do this. 

6.

7.


